IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-07 ms.tex
I added a simple temperature difference model.

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
\end{abstract}

@@

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption. with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

@@

>>>>

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
\end{abstract}

@@

\subsection{Mie Scattering Fit}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption. with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m. Also shown in the figure is the WFC3 amplitude from \citet{yang2015hstRotBD}. The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

@@

\subsection{Spot Model Fit}

Another simple model we attempt is a spot model - that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars.
In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
This time we model the data with two layers in local thermodynamic equilibrium (LTE) so that the flux is a ratio of two Planck functions.
We include a multiplicative constant to account for the geometric area ratio of the two temperature layers.
The two-layer model best-fits the data with a reduced chi-squared of 4.0, which is significantly disfavored as compared to the Mie scattering mode.
Furthermore, the 400 K temperature variation in the model is significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
\caption{The same data as in Figure \ref{fig:ampspec1821mie}. We fit the data as a temperature differential between the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
\end{centering}
\end{figure}
